Test RMD

### 2017-08-16 01_actor_careers/05_report.Rmd
JS pass

---
title: "How Old Actors?"
output: 
  html_document:
    code_folding: hide
---

@@

female_cdf = chart_data$female_actor_cdf
female_pdf = chart_data$female_actor
male_cdf = chart_data$male_actor_cdf
male_pdf = chart_data$male_actor
dir_cdf = chart_data$director_cdf %>% round(2)
dir_pdf = chart_data$director

@@

          chart.yAxis[0].setExtremes(0,`1`);
          data = `dir_cdf`;
          alert(data);
          <!--chart.series[0].setData(`JS(paste0("[", dir_cdf %>% paste(collapse = ","), "]"))`); -->
        };

>>>>

---
title: "Test RMD"
output: 
  html_document:
    code_folding: hide
---

@@

convert_js_vec = function(vec) {

  js_string = vec %>% round(2) %>% paste(collapse = ",")

  return(JS( paste0("[", js_string, "]") ))

}

female_cdf = chart_data$female_actor_cdf %>% convert_js_vec()
female_pdf = chart_data$female_actor %>% convert_js_vec()
male_cdf = chart_data$male_actor_cdf %>% convert_js_vec()
male_pdf = chart_data$male_actor %>% convert_js_vec()
dir_cdf = chart_data$director_cdf %>% convert_js_vec()
dir_pdf = chart_data$director %>% convert_js_vec()

@@

          chart.yAxis[0].setExtremes(0,`r 1`);
          var dat = `r JS(paste0("[", dir_cdf %>% paste(collapse=",") , "]") )`;
          alert(dat);
          chart.series[0].setData(dat);
        };
